Vegetation regrowth/encroachment (gjengroing)

### 2023-08-10 DRAFT_gjengroing.Rmd
Update DRAFT_gjengroing.Rmd
changes file paths to P:/...

```{r}
include_graphics('./DATA/images/gjengroing_schematic.jpg')
```

@@

```{r}
regions <- st_read('./DATA/regions.shp') %>%
  mutate(region = factor(region) )
# Rename regions with correct Norwegian characters
levels(regions$region) <- c("Østlandet", "Midt-Norge","Nord-Norge","Sørlandet","Vestlandet")
```

@@

```{r}
# Function to read in multiple files resulting from GEE exports
readVegHeightFiles <- function(uniqueString){
  dir <- './DATA/From_GEE/vegHeights/'
  files <- list.files(dir)[str_detect(list.files(dir), uniqueString)]
  #print(files)

>>>>

```{r}
include_graphics('P:/41201785_okologisk_tilstand_2022_2023/gjengroing/R_project/DATA/images/gjengroing_schematic.jpg')
```

@@

```{r}
regions <- st_read('P:/41201785_okologisk_tilstand_2022_2023/gjengroing/R_project/DATA/regions.shp') %>%
  mutate(region = factor(region) )
# Rename regions with correct Norwegian characters
levels(regions$region) <- c("Østlandet", "Midt-Norge","Nord-Norge","Sørlandet","Vestlandet")
```

@@

```{r}
# Function to read in multiple files resulting from GEE exports
readVegHeightFiles <- function(uniqueString){
  dir <- 'P:/41201785_okologisk_tilstand_2022_2023/gjengroing/R_project/DATA/From_GEE/vegHeights/'
  files <- list.files(dir)[str_detect(list.files(dir), uniqueString)]
  #print(files)
